Hardware-accelerated Rendering of Intersecting Volumes using Boolean Operations

### 2013-04-22 paper.tex
Elude to slicing method needing to generate a large amount of geometry every frame in abstract

% ========
% Abstract
% ========
\begin{abstract}
Rendering intersecting volumes is difficult because the renderer must alternate
between sampling from each volume to achieve the correct blending.  Methods for
rendering an arbitrary number of intersecting volumes on the GPU have been
developed, but they can require a significant amount of effort to implement.
This paper investigates implementing the simplest case, where two volumes
overlap, using familiar boolean operations and a traditional graphics library.
\end{abstract}

>>>>

% ========
% Abstract
% ========
\begin{abstract}
Rendering intersecting volumes is difficult because the renderer must alternate
between sampling from each volume to achieve the correct blending.  Methods for
rendering an arbitrary number of intersecting volumes on the GPU have been
developed, but they can require a large amount of geometry to be created every
frame, or may be difficult or time-consuming to implement.  This paper
investigates implementing the simplest case, where two volumes overlap, using
familiar boolean operations and a traditional graphics library.
\end{abstract}
